\newpage\newpage
\section{Place Recognition and Evaluation}
%\begin{itemize}
% \item \textbf{Compare the classification result L* with the true location for every image patch.}
% \item  \textbf{Count the number of times L* predicts the location correctly for all test images at each location.}
% \item  \textbf{Count the number of times L* predicts the location incorrectly for all test images at each location.}
% \item  \textbf{Report results as a confusion matrix.}
%\end{itemize}
The evaluation data sets for the four different locations are as follows:
\begin{itemize}
	\item{AVS laboratory:}
	$I = 19$ images.
	\item{ORCCA laboratory: }
	$I = 5$ images.
	\item{Corridor office: }
	$I = 10$ images.
	\item{Corridor ORCCA: }
	$I = 10$ images.
\end{itemize}

Where each image $I$ has associated a feature vector list $\bm{Y}_l \in [3072 \times D]$, 
and again $D=8$ is the dimensionality of the observed feature vector $\bm{y}_{l,r,p}$. 
With the evaluation data sets for each location readily available, 
the next step is to load the models chosen in part C 
($L_1$: AVS model with $M_1 = 6$ clusters,  
$L_2$: ORCCA model with $M_2 = 4$ clusters, 
$L_3$: corridor office model with $M_3 = 4$ clusters  and 
$L_4$: corridor ORCCA with $M_4 = 4$ clusters as well). 
Each loaded model $L$ is conformed by the vectors of the posterior hyper-parameter values 
corresponding to each $k \in M_i$.

For all the essential component feature $\bm{y}_{l,r,p}$ that conform one of the I images, 
%the log likelihood  $\log P( {\bm{y}_{l,r,p} \vline L}, \bm{Y}_l)$.
the sum of log likelihoods is computed assuming a given model L:  
\begin{equation}
{\sum\limits_{p=1}^{3072} \log P( {\bm{y}_{l,r,p} \vline L}, \bm{Y}_l)}
\end{equation}
If we repeat this computation for every location model $L$, 
we can see which of the models best explains the observed data $\bm{Y}_l$: 
\begin{equation}
L* = argmax_{L \in \{1,2,3,4\}} {\sum\limits_{p=1}^{3072} \log P( {\bm{y}_{l,r,p} \vline L}, \bm{Y}_l)}
\end{equation}

The classification results for each image I in every location are presented next, 
using the following nomenclature:
$$LM_{dictionary} =  [\textrm{corridor ORCCA, ORCCA, corridor office, AVS}] = [0, 1, 2, 3]$$
%where $LM$ refers to the dictionary of models. 
%And the results are as follows:
\begin{itemize}
	\item{AVS laboratory images classification results ($I = 19$ images): } \newline
	[ 2,  2,  3,  3,  3,  3,  3, 3,  2,  2,  3,  3,  2,  3,  0,  2,  3, 1, 2 ] \newline
	Occurrences: \{corridor ORCCA: 1, ORCCA: 1, corridor office: 7, \EditMC{AVS: 10}\}\newline
	Correct predictions: 10 / 19 $(\approx 52.6\%)$.\newline
	Incorrect predictions: 9 / 19.
	%Occurrences (entry: counts) :  \{0.0: 1, 1.0: 1, 2.0: 7, 3.0: 10\}
	\item{ORCCA laboratory images classification results: ($I = 5$ images.)}\newline
	[ 1,  1,  3,  1,  3 ] \newline
	Occurrences:  \{\EditMC{ORCCA: 3},  AVS: 2\} \newline
	Correct predictions: 3 / 5 $(\equiv 60.0\%)$.\newline
	Incorrect predictions: 2 / 5.
	%Occurrences:  {1.0: 3, 3.0: 2}
	\item{Corridor office images classification results ($I = 10$ images): }\newline
	[ 1,  3,  1,  2,  1,  1,  1,  2,  1,  2 ]\newline
	Occurrences:  \{\EditHPS{ORCCA: 6}, corridor office: 3, AVS: 1\} \newline
	Correct predictions: 3 / 10 $(\equiv 30.0\%)$.\newline
	Incorrect predictions: 7 / 10.
	%Occurrences:  {1.0: 6, 2.0: 3, 3.0: 1}
	\item{Corridor ORCCA images classification results ($I = 10$ images):}\newline
	[ 3,  3,  2,  1,  2,  3,  3,  3,  1,  1 ]\newline
	Occurrences:  \{ORCCA: 3, corridor office: 2,  \EditHPS{AVS: 5}\} \newline
	Correct predictions: 0 / 10.\newline
	Incorrect predictions: 10 / 10.
\end{itemize}

The reported results show that place recognition is successfully achieved for the 
AVS laboratory and for the ORCCA laboratory. 
Nevertheless, an incorrect location is inferred for both corridors. 
One reason that could explain this fact is the lack of distinctive features in any kind of corridor in general. 
In the case of the office corridor, the correct location is predicted a few times but not generally. 
In contrast, for the corridor ORCCA, the right location is never inferred. Further, the very few occurrences 
for which the corridor ORCCA is chosen incorrectly in the images from other locations 
(i.e. index 0 in the classification results) indicates that there might be 
something anomalous in the learnt model for the corridor ORCCA itself. It seems to be conformed by a very particular mixture of 
components with responsibilities that are not reflective of almost any of the training images, not even the ones 
from the true corridor ORCCA location. 







